HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-03-18 paper/main.tex
spellcheck

In non-configurational languages, the relationship between the
governing and dependent units is often expressed using morphological
properties of the dependents instead of their ordering
(this holds especially for the verb and its modifiers,
less so for components of noun phrases). Errors in morphology
should be expressed on the atomic units, so HUME can behave differently
on configurational vs. non-configurational languages.

@@

We proceed to detailing how judgements on the semantic units
of the source are aggregated into a composite score. We start by taking a parsiminous approach
%While future extensive empirical evaluation with HUME and its application to MT
%system tuning may suggest more complex definition,
%as a starting point we take a parsimonious approach,
and compute an accuracy score.

@@

Concretely, let $s = (w_1,\ldots,w_n)$ be a source sentence, $t = (w'_1,\ldots,w'_n)$ a translation,
and $A \subset 2^{s \times t}$ a many-to-many word alignment between them.
If $u$ is a semantic unit in $s$, whose yield is $yld(u)$, we define the aligned text in
$t$ to be $a(u)=\bigcup_{(x_s,x_t) \in A \wedge x_s \cap yld(u) \neq \emptyset} x_t \subset t$.
Where $a(u)$ is discontiguous in the text, words between the left
and right boundaries of $a(u)$ which are not contained in it (intervening words)
are presented in a smaller red font.
Intervening words are likely to change the meaning of the translation
of $u$, and thus should be paid attention to when considering whether the translation
is correct or not.

@@

There are however a number of other serious consequences on focussing on verbal
predicates. We conducted an analysis of the English UCCA Wikipedia
corpus (5324 sentences)
in order to assess the impact of the following problems: 
\\
\begin{inparadesc}
\item[Copula clauses] are treated in HMEANT simply as instances of the main verb ``be'', which
generally does not convey the meaning of these clauses. They appear in 21.7\% of the sentences,
according to conservative estimates that only considers non-auxilliary instances of ``be''.
\\
\item[Nominal argument structures,] which are ignored by  HMEANT are in fact highly
pervasive, appearing in 48.7\% of the sentences.
\\
\item[Linkers] expressing an inter-relation between
clauses (mainly discourse markers and coordinating conjunctions) appear in 56\% of the
sentences\footnote{Argument structures and linkers are explicitly marked in UCCA. We identified non-auxilliary instances of ``be'' and nouns using the NLTK standard tagger. Nominative argument structures are here defined as Scenes whose main relation is headed by a noun.}.
\end{inparadesc}

@@

In HMEANT, there are no guidelines as to when to propagate and error. In HUME,
errors are localised as much as possible to where they occur, by the separation of atomic and structural nodes. This allows us to calculate more acurately the total score of the sentence.

>>>>

In non-configurational languages, the relationship between the
governing and dependent units is often expressed using morphological
properties of the dependants instead of their ordering
(this holds especially for the verb and its modifiers,
less so for components of noun phrases). Errors in morphology
should be expressed on the atomic units, so HUME can behave differently
on configurational vs. non-configurational languages.

@@

We proceed to detailing how judgements on the semantic units
of the source are aggregated into a composite score. We start by taking a parsimonious approach
%While future extensive empirical evaluation with HUME and its application to MT
%system tuning may suggest more complex definition,
%as a starting point we take a parsimonious approach,
and compute an accuracy score.

@@

Concretely, let $s = (w_1,\ldots,w_n)$ be a source sentence, $t = (w'_1,\ldots,w'_n)$ a translation,
and $A \subset 2^{s \times t}$ a many-to-many word alignment between them.
If $u$ is a semantic unit in $s$, whose yield is $yld(u)$, we define the aligned text in
$t$ to be $a(u)=\bigcup_{(x_s,x_t) \in A \wedge x_s \cap yld(u) \neq \emptyset} x_t \subset t$.
Where $a(u)$ is discontinuous in the text, words between the left
and right boundaries of $a(u)$ which are not contained in it (intervening words)
are presented in a smaller red font.
Intervening words are likely to change the meaning of the translation
of $u$, and thus should be paid attention to when considering whether the translation
is correct or not.

@@

There are however a number of other serious consequences on focusing on verbal
predicates. We conducted an analysis of the English UCCA Wikipedia
corpus (5324 sentences)
in order to assess the impact of the following problems: 
\\
\begin{inparadesc}
\item[Copula clauses] are treated in HMEANT simply as instances of the main verb ``be'', which
generally does not convey the meaning of these clauses. They appear in 21.7\% of the sentences,
according to conservative estimates that only considers non-auxiliary instances of ``be''.
\\
\item[Nominal argument structures,] which are ignored by  HMEANT are in fact highly
pervasive, appearing in 48.7\% of the sentences.
\\
\item[Linkers] expressing an inter-relation between
clauses (mainly discourse markers and coordinating conjunctions) appear in 56\% of the
sentences\footnote{Argument structures and linkers are explicitly marked in UCCA. We identified non-auxiliary instances of ``be'' and nouns using the NLTK standard tagger. Nominative argument structures are here defined as Scenes whose main relation is headed by a noun.}.
\end{inparadesc}

@@

In HMEANT, there are no guidelines as to when to propagate and error. In HUME,
errors are localised as much as possible to where they occur, by the separation of atomic and structural nodes. This allows us to calculate more accurately the total score of the sentence.
